The problem and promise of scale in animal social multilayer networks

### 2020-02-09 paper/manuscript.Rmd
P3 move persp

In contrast to spatial networks, where nodes represent spatial locations that
are fixed in space, movement networks can represent continuous and simultaneous
movement trajectories of multiple animals. Continuous collection of animal
relocation data using GPS technology can be used to measure how groups of
animals make collective movement decisions in the context of their local
environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A
collective movement layer could constitute similarity in movement for dyads
(Long et al. 2014) or groups (Bode et al. 2011). This movement layer could be
made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale
(global migration: Flack et al. 2018). Another potential application would be to
generate social networks during times when animals are engaged in different
behaviours, including traveling, interacting, or foraging (e.g. Muller et al.
2018; Finn et al. 2019) and construct a multilayer network based on
behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019).
Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations (see Hughey et al. 2018).

>>>>

In contrast to spatial networks, where nodes represent spatial locations that
are fixed in space, movement networks can represent continuous and simultaneous
movement trajectories of multiple animals. In a recent study of vulturine 
gunieafowl (Acryllium vulturinum), GPS movement data were used to generate 
monolayer association networks within a multilayer network (Papageorgiou et al. 2019). 
However, despite potential to generate networks in different spatial or social contexts, 
layers in the multilayer network represented social associations within and 
between groups. Continuous collection of animal relocation data using GPS 
technology can be used to measure how groups of
animals make collective movement decisions in the context of their local
environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A
collective movement layer could constitute similarity in movement for dyads
(Long et al. 2014) or groups (Bode et al. 2011). This movement layer could be
made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale
(global migration: Flack et al. 2018). Our case study integrates variation 
in temporal and spatial scale to assess the role of scale in predicting 
multilayer networks. As one might expect, we found increasing spatial 
scale results in saturation of potential social connections (Figure 3), 
while increasing temporal scale had little effect on habitat-specific 
networks (Figure 5). Another potential application would be to
generate social networks during times when animals are engaged in different
behaviours, including traveling, interacting, or foraging (e.g. Muller et al.
2018; Finn et al. 2019) and construct a multilayer network based on
behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019).

Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations (Hughey et al. 2018).
